### 2014-09-15 PrivacyProtection-2014-09-09.tex
finished interest description of citizens

@@

\subsubsection{IT-Systems}

@@

\subsubsection{Humans}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak

@@

\subsubsection{IT-Systems}
\label{subsubsection:it-systems}

@@

\subsubsection{Humans}
\label{subsubsection:humans}

This section outlines the human actors previously introduced within the IT system architecture (\ref{subsubsection:it-systems}).
It is described which individual interests they have invested in monitoring systems comparable to the Live+Gov system. 
Also the additional actor \textit{Criminal} is introduced as an possible obstacle.

\textbf{Citizen:}
Citizens who take part in such urban monitoring systems share privacy sensitive data about themselves. 
They do it out of freewill and with consent to certain agreements on secrecy and proportionality.
So naturally they are interested in not having private information about them revealed to unknown third parties.
This would interfere with their ability to control such information, thus they cannot exercise privacy (according to Fried) anymore.

Beyond that, they share information with trust in the legitimate and proportional use of that information. 
Citizens expect their data is only used for public improvement within the agreed bounds.
They do not expect that their data is used for illegitimate purposes like scoring procedures, which could have a possible negative effect for them.

In general, Citizens are not interested in negative results for themselves.
This for financial loss. 
Local Authorities pay System Providers for their services.
Typically Local Authorities capitalize themselves via taxes.
So Citizens also have financial interests invested in the monitoring system.

In short, Citizens are interested in ...
\begin{itemize}
\item ... confidential use of privacy sensitive data
\item ... legitimate use of privacy sensitive data
\item ... proportional use of privacy sensitive data
\item ... successful use of privacy sensitive data
\end{itemize}

\textbf{System Provider:} Lorem Ipsum

\textbf{Local Authority:} Lorem Ipsum

\textbf{Criminal:} Lorem Ipsum
